POMDP comparisons across sigma_m, sigma_g

### 2017-12-28 appendix/appendix_harvestfirst.Rmd
index fun
larger discount for faster convergence

Utility (reward) function:

```{r}
reward_fn <- function(x,h) pmin(x,h)
discount <- 0.99
```

@@

This uses a generic optimization routine to find the stock size at which the maximum growth rate is achieved.

```{r}
## A generic routine to find stock size (x) which maximizes 
## growth rate (f(x,0) - x, where x_t+1 = f(x_t))
S_star <- optimize(function(x) -f(x,0) + x / discount, 
                   c(0, 2*K))$minimum
```

@@

@@

## POMDP solution (slow, >10,000 seconds per scenario, & memory intensive)
system.time(
  alphas <- 
    parallel::mclapply(1:length(models), 
    function(i){
      log_data <- data.frame(model = "gs", 
                             r = r, 
                             K = K, 
                             sigma_g = meta[i,"sigma_g"][[1]], 
                             sigma_m = meta[i,"sigma_m"][[1]], 
                             noise = "normal",
                             scenario = meta[i, "scenario"][[1]])

@@

>>>>

Utility (reward) function.  (Note that setting a smaller discount will take longer to converge to smooth POMDP solution, but result in `S_star` closer to the simple `B_MSY`.)

```{r}
reward_fn <- function(x,h) pmin(x,h)
discount <- 0.95
```

@@

This uses a generic optimization routine to find the stock size at which the maximum growth rate is achieved.  (Note that this also depends on the discount rate since future profits are worth proportionally less than current profits).

```{r}
## A generic routine to find stock size (x) which maximizes 
## growth rate (f(x,0) - x, where x_t+1 = f(x_t))
S_star <- optimize(function(x) -f(x,0) + x / discount, 
                   c(0, 2*K))$minimum
S_star
```

@@

```{r}
index <- function(x, grid) map_int(x, ~ which.min(abs(.x - grid)))

@@

## POMDP solution 
## (slow, >10,000 seconds per scenario for discount ~ 0.95;
## needs much longer for discount ~ 0.99)
system.time(
  alphas <- 
    parallel::mclapply(1:length(models), 
    function(i){
      log_data <- data.frame(model = "gs", 
                             r = r, 
                             K = K, 
                             sigma_g = meta[i,"sigma_g"][[1]], 
                             sigma_m = meta[i,"sigma_m"][[1]], 
                             noise = "normal",
                             scenario = meta[i, "scenario"][[1]])

@@

```{r}
pomdp_policies %>% 
  ggplot(aes(state, escapement, col=policy)) + 
  geom_line()  + 
  coord_cartesian(xlim = c(0,K), ylim = c(0, .8))
```
